### 2013-12-05 manuscripts/reply/short-reply.tex
Adding references.
Adding references as examples of taxonomic uncertainty in the
Philippines.

\subsection*{Additional thoughts on empirical priors in Bayesian model choice}
Given the theoretical and practical issues with empirical Bayes approaches to
Bayesian model choice discussed in the proceeding sections, it is quite clear
why one should use caution before overly criticizing an investigator's choice
of priors after having seen the resulting posterior.
%In a strictly Bayesian world, this is cheating.
As discussed by \citet{Oaks2012}, prior to analyzing the data, there was a
large amount of uncertainty regarding the divergence times of the 22 population
pairs under study.
Two of these pairs represent distinct species, and the taxonomy of many groups
in the Philippines has repeatedly been shown to mask deeply divergent lineages
\citep{RafeDiesmosAlcala2008,Linkem2010,Siler2010,Welton2010,Siler2011HerpMonographs,
    Siler2011,Siler2012,RafeStuart2012,LinkemBrown2013}.
% \citet{Oaks2012} also discuss how uniform priors on postive real-valued parameters make
% it difficult for investigators to express their prior uncertainty without
% putting high prior density in regions of improbable parameter space.
The alternative to priors that reflect prior uncertainty, as shown above, is to
risk excluding the truth before performing the analysis.

>>>>

\subsection*{Additional thoughts on empirical priors in Bayesian model choice}
Given the theoretical and practical issues with empirical Bayes approaches to
Bayesian model choice discussed in the proceeding sections, it is quite clear
why one should use caution before overly criticizing an investigator's choice
of priors after having seen the resulting posterior.
%In a strictly Bayesian world, this is cheating.
As discussed by \citet{Oaks2012}, prior to analyzing the data, there was a
large amount of uncertainty regarding the divergence times of the 22 population
pairs under study.
Two of these pairs represent distinct species, and the taxonomy of many groups
in the Philippines has repeatedly been shown to mask deeply divergent lineages
\citep{RafeDiesmosAlcala2008,Linkem2010,Siler2010,Welton2010,Siler2011HerpMonographs,
Siler2011,Siler2012,RafeStuart2012,LinkemBrown2013,Rafe2013AREES,Siler2014kikuchii}.
% \citet{Oaks2012} also discuss how uniform priors on postive real-valued parameters make
% it difficult for investigators to express their prior uncertainty without
% putting high prior density in regions of improbable parameter space.
When limited to uniformly distributed priors, the alternative to priors that
reflect prior uncertainty, as shown above, is to risk excluding the truth
before performing the analysis.
